### 2021-04-22 docs/manuscript/PLOS-MSc-Thesis.tex
Add asterisk to main author

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris Rodríguez-Rey\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1*},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris Rodríguez-Rey\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip
